---
title: "Assignment 5"
author: "Parth Thaker"
date: "2023-10-28"
output: html_document
---

```{r}

library(fpp)
library(fpp2)
library(TTR)
library(readxl)

# Reading Data 

df <- read_excel("Sunspots_Dataset.xlsx")

# Converting to Time Series Data 

df_TSer = ts(df$`Monthly Mean Total Sunspot Number`,start=c(2011,1), end=c(2021,1),frequency = 12)

# Attributes and Structure

attributes(df_TSer)
str(df_TSer) 

```

# Decomposition 

## Seasonal Decomposition of Time Series by Loess (STL) Method

```{r}

head(df_TSer)
plot(df_TSer)
stl_decomp <- stl(df_TSer,s.window ="periodic")
plot(stl_decomp)
attributes(stl_decomp)

```

# Taking out Seasonal Adjustment 

```{r}

seasadj(stl_decomp)

```

# Plot a line on the graph

```{r}

plot(df_TSer)
lines(seasadj(stl_decomp), col= "Red")

```

# Default period forecast

```{r}

df_TSer_forecast <- forecast(stl_decomp)

```
# Forecasting the Seasonally Adjusted Decomposed Time Series

```{r}
df_TSer_forecast <- forecast(stl_decomp,h=20)
plot(df_TSer_forecast)

```

## Plotting the seasonal component

```{r}

plot(stl_decomp$time.series[, "seasonal"], main="Seasonal Component")

```

## Plotting the trend component

```{r}

plot(stl_decomp$time.series[, "trend"], main="Trend Component")

```

## Plotting the remainder component
```{r}

plot(stl_decomp$time.series[, "remainder"], main="Remainder (Residual) Component")

```

# Other Method Of Decomposition

```{r}

decomp_elec <- decompose(df_TSer)
plot(decomp_elec)

```


# Each one shows different attributes 

```{r}

attributes(decomp_elec)
seasadj(decomp_elec)

```


## Using Decompose Function

```{r}

df_TSer_decompose <- decompose(df_TSer)
attributes(df_TSer_decompose)
plot(df_TSer_decompose)


```

# Seasonal Adjustment

```{r}
df_TSer_decompose_seasadj = seasadj(df_TSer_decompose)
plot(df_TSer_decompose_seasadj)

```

# Plotting Line Seasonally Adjusted Decomposed TS with the original Time Series

```{r}

plot(df_TSer)
lines(df_TSer_decompose_seasadj, col="purple")

```
















